Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

We now prove the first claim of statement (2), namely, $\bm{t}\in \J(R_1',...,R_{k-2}')$. Consider the $k$-tuple $(r_1,...,r_{k-2},h,v)\in \J_1$ given in statement (2). By definition of $\J_1$, segments $h$ and $v$ both cross each of the rectangles $r_1,..., r_{k-2}$. According to our earlier discussion, $h$ and $v$ must also cross each of the trimmed rectangles $r_1',..., r_{k-2}'$. Hence, the intersection of $h$ and $v$ is a point covered by each of $r_1',..., r_{k-2}'$. Hence, $\bigcap_{i = 1}^{k-2}r_i'$ cannot be empty. Therefore, $\bm{t} = (r_1', ..., r_{k-2}')$ is a result tuple in $\J(R_1',...,R_{k-2}')$.

@@

Next, we prove the second claim, namely, $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$. It suffices to show only the former due to symmetry. To prove $h \in \dcross_H(\bm{t})$, we need to argue that $h$ crosses $\gbot(\bm{t})$ and $B_\bm{t}$. The first part, $h$ crossing $\gbot(\bm{t})$, is done because, as already explained, $h$ crosses each of $r_1', ..., r_{k-2}'$, and $\gbot(\bm{t})$ is one of those $k-2$ rectangles. To prove that $h$ crosses $B_\bm{t}$, first note that $B_\bm{t}$ (which is the intersection of $r_1', ..., r_{k-2}'$) is covered by $\gbot(\bm{t})$. The fact that $h$ crosses $\gbot(\bm{t})$ indicates that the y-range of $h$ contains that of $B_\bm{t}$. Hence, either $h$ is disjoint with $B_\bm{t}$ or $h$ crosses $B_\bm{t}$. However, $h$ cannot be disjoint with $B_\bm{t}$ because, as shown earlier, the intersection of $h$ and $v$ falls in $B_\bm{t}$. It thus follows that $h$ crosses $B_\bm{t}$.

>>>>

We now prove the first claim of statement (2), namely, $\bm{t}\in \J(R_1',...,R_{k-2}')$. Consider the $k$-tuple $(r_1,...,r_{k-2},h,v)\in \J_1$ given in statement (2). By definition of $\J_1$, segments $h$ and $v$ both cross each of the rectangles $r_1,..., r_{k-2}$. According to our earlier discussion, $h$ and $v$ must also cross each of the trimmed rectangles $r_1',..., r_{k-2}'$. Hence, the intersection of $h$ and $v$ is a point covered by each of $r_1',..., r_{k-2}'$. Hence, $B_\bm{t} = \bigcap_{i = 1}^{k-2}r_i'$ cannot be empty, meaning that $\bm{t} = (r_1', ..., r_{k-2}') \in \J(R_1',...,R_{k-2}')$.

@@

Next, we prove the second claim, namely, $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$. It suffices to show only the former due to symmetry. To prove $h \in \dcross_H(\bm{t})$, we need to argue that $h$ crosses $\gbot(\bm{t})$ and $B_\bm{t}$. The first part, $h$ crossing $\gbot(\bm{t})$, is done because, as already explained, $h$ crosses each of $r_1', ..., r_{k-2}'$, and $\gbot(\bm{t})$ is one of those $k-2$ rectangles. To prove that $h$ crosses $B_\bm{t}$, first note that $B_\bm{t}$ is covered by $\gbot(\bm{t})$. The fact of $h$ crossing $\gbot(\bm{t})$ indicates that the x-range of $h$ contains that of $B_\bm{t}$. Hence, either $h$ is disjoint with $B_\bm{t}$ or $h$ crosses $B_\bm{t}$. However, $h$ cannot be disjoint with $B_\bm{t}$ because as explained earlier $h \cap v$ falls in $B_\bm{t}$. It thus follows that $h$ crosses $B_\bm{t}$.
